Compositional equivalences based on Open pNets

### 2020-03-05 2016-Weak-FH-Bisim/WeakBisim.tex
Abstract + compositional
signature/affiliation Ludo

\title{Compositional equivalences based on Open pNets
%\thanks{This work was partially funded by the Associated Team FM4CPS
%  between INRIA and ECNU, Shanghai}
}
\author{Ludovic Henrio}

@@

>>>>

\title{Compositional equivalences based on Open pNets
%\thanks{This work was partially funded by the Associated Team FM4CPS
%  between INRIA and ECNU, Shanghai}
}
\author{Ludovic Henrio}
\address{Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France.}
\email{ludovic.henrio@cnrs.fr}

@@

Amon these properties we show compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
